Exacerbated by the Pandemic: Analyzing the Impact of COVID-19 on Mortality Among Toronto's Homeless by Gender Disparities

### 2024-03-16 paper/paper.qmd
Update paper.qmd

The analysis will be conducted in R (R Core Team 2020) and will utilize an array of packages such as tidyverse (Wickham et al. 2019), readr (Wickham, Hester, and Bryan 2024), dplyr (Wickham et al. 2021), and opendatatoronto (Gelfand 2020) for data manipulation and analysis. All visualizations in this report are generated through ggplot2 (Wickham 2016), with tables crafted using kableExtra (Zhu 2021).

>>>>

The analysis will be conducted in [@citeR] and will utilize an array of packages such as [@citetidyverse], [@citereadr], [@citedplyr], and [@citeopendatatoronto] for data manipulation and analysis. All visualizations in this report are generated through [@citeggplot2], with tables crafted using [@citekableExtra].
